Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-11-11 xrb2/paper.tex
Switch to CGS

\begin{figure}[t]
	\centering
	\plotone{flame_speeds_rotation.pdf} % Not certain what style we want for the plot here
	\caption{\label{fig:flame_speeds_1} Flame front position vs.\ time for the 500 Hz and 1000 Hz runs. The dashed lines
		show quadratic least-squares fits to the data for $t \gtrsim 20~\mathrm{ms}$.}
\end{figure}

\begin{figure}[t]
	\centering
	{\color{red} Placeholder for the flame speed plot that shows temperature dependence}
	\caption{\label{fig:flame_speeds_2} Flame front position vs.\ time for the three 500 Hz runs with
		$T_{star} \leq 3 \times 10^8~\mathrm{K}$. The dashed lines show quadratic least-squares fits to the data
		for $t \gtrsim 20~\mathrm{ms}$.}
\end{figure}

Figures~\ref{fig:flame_speeds_1} and \ref{fig:flame_speeds_2} give position vs.\ time for our runs, with the former showing dependence
on rotation rate and the latter on the neutron star temperature. As some of the runs (in particular the $\tt{flame\_wave\_3E8}$ run) exhibit
significant accelerations, we fit a quadratic curve to each set of data and calculate the acceleration and initial velocity from the fit
parameters. These results are given in Table~\ref{table:flame_speeds}. We also include the flame speed at $t = 100~\mathrm{ms}$ extrapolated
from the fit.

We found in \citet{flame_wave1} that the flame speed $s$ obeys:
\begin{equation}
	s \appropto L_R (\epsdot)^{\half} \propto \frac{(\epsdot)^{\half}}{\Omega}
\end{equation}
where $\epsdot$ is the specific energy generation rate and $L_R$ is the Rossby length. This was consistent with the results of
\citet{cavecchi:2013}, who noted that the flame speeds in their simulations scaled with the Rossby length. As seen in
Figure~\ref{fig:flame_speeds_1}, there is no obvious inverse scaling with rotation rate in this set of runs. We observed earlier,
however, that nuclear reactions progress more quickly at the higher rotation rate. This results in a higher $\enucdot$ --- up to 4
to 6 times higher near the burning front after the flame ignites --- which may counteract the reduction in flame speed from the
increased Coriolis confinement. We also observe that 500 Hz run accelerates faster than the 1000 Hz run, which appears to experience a
small deceleration at early times. This disparity could be due to the 500 Hz flame taking more time to develop fully and reach higher
burning rates, resulting in an $\epsdot$ increase over time. It may also be a direct result of the difference in Coriolis force. \MarginPar{Do we have other ideas why?}

@@

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:flame_speeds} Flame speed and acceleration values measured for each simulation. $s_0$ is the speed at $t = 0~\mathrm{ms}$, and $s_{100}$ is the speed at $t = 100~\mathrm{ms}$.}
	\tablehead{\colhead{run} & \colhead{$s_0$ (km s$^{-1}$)} & \colhead{$s_{100}$ (km s$^{-1}$)} & \colhead{$a$ (km s$^{-2}$)}} 
	\startdata
	{\tt flame\_wave\_500}      & $3.08 \pm 0.01$ & $3.62 \pm 0.02$ & $5.41 \pm 0.19$ \\
	{\tt flame\_wave\_1000}     & $3.41 \pm 0.01$ & $3.31 \pm 0.02$ & $-1.03 \pm 0.13$ \\
	{\tt flame\_wave\_500\_2E8} & $3.76 \pm 0.02$ & $\sim 3.93$ & $1.74 \pm 0.17$ \\
	{\tt flame\_wave\_500\_3E8} & $5.29 \pm 0.10$ & $\sim 41.0$ & $357.4 \pm 1.5$ \\
	\enddata
	%
\end{deluxetable}

>>>>

\begin{figure}[t]
	\centering
	\plotone{flame_speeds_rotation.pdf}
	\caption{\label{fig:flame_speeds_1} Flame front position vs.\ time for the standard ($10^8~\mathrm{K}$) 500 Hz and 1000 Hz runs. The dashed lines
		show quadratic least-squares fits to the data for $t \gtrsim 0.02~\mathrm{s}$.}
\end{figure}

\begin{figure}[t]
	\centering
	{\color{red} Placeholder for the flame speed plot that shows temperature dependence}
	\caption{\label{fig:flame_speeds_2} Flame front position vs.\ time for the three 500 Hz runs with
		$T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$. The dashed lines show quadratic least-squares fits to the data
		for $t \gtrsim 0.02~\mathrm{s}$.}
\end{figure}

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:flame_speeds} Flame speed and acceleration values measured for each simulation. $s_0$ is the speed at $t = 0~\mathrm{ms}$.}
	\tablehead{\colhead{run} & \colhead{$s_0$ (cm s$^{-1}$)} & \colhead{$a$ (cm s$^{-2}$)}} 
	\startdata
	{\tt flame\_wave\_500}      & $(3.08 \pm 0.01) \times 10^5$ & $(5.41 \pm 0.19) \times 10^5$ \\
	{\tt flame\_wave\_1000}     & $(3.41 \pm 0.01) \times 10^5$ & $(-1.03 \pm 0.13) \times 10^5$ \\
	{\tt flame\_wave\_500\_2E8} & $(3.76 \pm 0.02) \times 10^5$ & $(1.74 \pm 0.17) \times 10^5$ \\
	{\tt flame\_wave\_500\_3E8} & $(5.29 \pm 0.10) \times 10^5$ & $(3.57 \pm 0.02) \times 10^7$ \\
	\enddata
	%
\end{deluxetable}

Figures~\ref{fig:flame_speeds_1} and \ref{fig:flame_speeds_2} give position vs.\ time for our runs, with the former showing dependence
on rotation rate and the latter on the neutron star temperature. As some of the runs (in particular the $\tt{flame\_wave\_3E8}$ run) exhibit
significant accelerations, we fit a quadratic curve to each set of data and calculate the acceleration and initial velocity from the fit
parameters. These results are given in Table~\ref{table:flame_speeds}.

We found in \citet{flame_wave1} that the flame speed $s$ obeys:
\begin{equation}
	s \appropto L_R (\epsdot)^{\half} \propto \frac{(\epsdot)^{\half}}{\Omega}
\end{equation}
where $\epsdot$ is the specific energy generation rate and $L_R$ is the Rossby length. This was consistent with the results of
\citet{cavecchi:2013}, who noted that the flame speeds in their simulations scaled with the Rossby length. As seen in
Figure~\ref{fig:flame_speeds_1}, there is no obvious inverse scaling with rotation rate in this set of runs. We observed earlier,
however, that nuclear reactions progress more quickly at the higher rotation rate. This results in a higher $\enucdot$ --- up to 4
to 6 times higher near the burning front after the flame ignites --- which may counteract the reduction in flame speed from the
increased Coriolis confinement. We also observe that 500 Hz run accelerates faster than the 1000 Hz run, which appears to experience a
small deceleration at early times. \MarginPar{This is speculative -- do we have a clear idea why?} This disparity may be a direct result
of the difference in Coriolis force. It could also be due to the 500 Hz flame taking more time to develop fully and reach higher burning
rates, resulting in an $\epsdot$ increase over time.

@@
